The Implementation of China’s Overseas NGO Law and the Operating Space for International Civil Society

### 2023-12-02 manuscript/manuscript.qmd
Minor edits to case study table + add table to repo

```{r fig-timing-local, fig.width=6, fig.height=3, out.width="80%"}
#| include: true
#| echo: false
#| fig-cap: "Expectation (or average) of posterior predictive distributions 
#|   from model with interaction between local connections and time since 
#|   January 2017. These predictions take into account single-province and 
#|   nationwide predictions and represent the overall conditional average 
#|   geographic range for INGOs over time across, conditional on local 
#|   connections. Shaded regions show the 50%, 80%, and 95% credible intervals"
epreds_timing_local |>
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |>
  ggplot(aes(x = years_since_law, y = prop_to_provinces(.epred))) +
  stat_lineribbon(
    .width = c(0.5, 0.8, 0.95),
    alpha = 0.35, fill = clrs[6], color = clrs[6]
  ) +
  scale_y_continuous(
    breaks = seq(0, 32, 8),
    sec.axis = sec_axis(
      trans = ~ provinces_to_prop(.),
      name = "Proportion of provinces",
      breaks = seq(0, 1, 0.25),
      labels = label_percent()
    )
  ) +
  guides(fill = "none") +
  labs(
    x = NULL, y = "Expected provinces",
    title = "Expected count of provinces across local connections",
    subtitle = "Expectation of posterior predictions"
  ) +
  coord_cartesian(ylim = c(1, 32)) +
  facet_wrap(vars(local_connect)) +
  theme_ongo()
```

@@

compare_table <- read_csv("data/manual_data/table_case_study.csv")

compare_table |> 
  gt() |> 
#  cols_width(Issue ~ gt_pct(20), Examples ~ gt_pct(50)) |> 
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) |>
  opts_theme() |> 
  tab_options(
    quarto.disable_processing = TRUE
  )
```

@@

@table-case-study summarizes the comparison of the cases of TNC and Greenpeace. The case study shows that in addition to the correlation of issue area and operational space found in the quantitative model, the dimension of relationship with the government also exerts influence on the contentious level and restrictions INGOs can face, revealing the potential patterns of differential treatment INGOs can receive in the *de facto* implementation of the law. Greenpeace also showed high organizational flexibility in the face of high legal barriers with the ONGO law : despite the various drawbacks discussed above, they were still able to keep conducting programs in China. A more evasive group of INGOs after the ONGO law would be those not having the same level of flexibility as Greenpeace and have left China either not choosing to seek registration or failed to do so and not able file temporary activities constantly. The variance in organizational flexibility can be worthy of further research.

>>>>

```{r fig-timing-local, fig.width=6, fig.height=3, out.width="80%"}
#| include: true
#| echo: false
#| fig-cap: "Expectation (or average) of posterior predictive distributions 
#|   from model with interaction between local connections and time since 
#|   January 2017. These predictions take into account single-province and 
#|   nationwide predictions and represent the overall conditional average 
#|   geographic range for INGOs over time across, conditional on local 
#|   connections. Shaded regions show the 50%, 80%, and 95% credible intervals"

epreds_timing_local |>
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |>
  ggplot(aes(x = years_since_law, y = prop_to_provinces(.epred))) +
  stat_lineribbon(
    .width = c(0.5, 0.8, 0.95),
    alpha = 0.35, fill = clrs[6], color = clrs[6]
  ) +
  scale_y_continuous(
    breaks = seq(0, 32, 8),
    sec.axis = sec_axis(
      trans = ~ provinces_to_prop(.),
      name = "Proportion of provinces",
      breaks = seq(0, 1, 0.25),
      labels = label_percent()
    )
  ) +
  guides(fill = "none") +
  labs(
    x = NULL, y = "Expected provinces",
    title = "Expected count of provinces across local connections",
    subtitle = "Expectation of posterior predictions"
  ) +
  coord_cartesian(ylim = c(1, 32)) +
  facet_wrap(vars(local_connect)) +
  theme_ongo()
```

@@

compare_table <- read_csv(here::here("data", "manual_data", "table-case-study.csv"))

compare_table |> 
  gt(rowname_col = "Characteristic") |> 
  cols_width(Characteristic ~ gt_pct(20), everything() ~ gt_pct(30)) |>
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) |>
  tab_style(
    style = cell_text(v_align = "top", weight = "bold"),
    locations = cells_stub()
  ) |>
  opts_theme() |> 
  tab_options(
    quarto.disable_processing = TRUE
  )
```

@@

@tbl-case-study summarizes the comparison of the cases of TNC and Greenpeace. The case study shows that in addition to the correlation of issue area and operational space found in the quantitative model, the dimension of relationship with the government also exerts influence on the contentious level and restrictions INGOs can face, revealing the potential patterns of differential treatment INGOs can receive in the *de facto* implementation of the law. Greenpeace also showed high organizational flexibility in the face of high legal barriers with the ONGO law : despite the various drawbacks discussed above, they were still able to keep conducting programs in China. A more evasive group of INGOs after the ONGO law would be those not having the same level of flexibility as Greenpeace and have left China either not choosing to seek registration or failed to do so and not able file temporary activities constantly. The variance in organizational flexibility can be worthy of further research.
